---
title: "Figure 1 Composition of gut bacteria in the JXB (Jiaxing Black) and DLY (Duroc × Landrace × Yorkshire) pigs (N = 5 for each group)."
author: "Liang Huang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Set output directory
output_dir="./"
```


# a & b.Alpha diversity (shannon and simpson)

(A) The differences in alpha diversity between the two pig breeds are shown by the Shannon and (B) Simpson indices.

```{r }
library(phyloseq)
library(vegan)
library(xlsx)
file="./metagenomic raw data (phylum).xlsx"
meta=read.xlsx(file,1,header=T,row.names=1)
meta=meta[,c(1:10)]
meta=t(meta)
meta=as.data.frame(meta)
group=read.xlsx(file,2,header=T,row.names=1)



shannon <- diversity(meta, index = "shannon")
shannon=as.data.frame(shannon)
df <- data.frame(shannon, Group = group$group)
write.xlsx(df,"./alpha_shannon.xlsx")


simpson <- diversity(meta, index = "simpson")
simpson=as.data.frame(simpson)
df <- data.frame(simpson, Group = group$group)
write.xlsx(df,"./alpha_simpson.xlsx")

# This figure is manually drawn by Graph Pad using data above.
```


# c PCoA and PLS-DA analysis

(C) Principal coordinate analysis (PCoA) and (D) partial least squares discriminant analysis (PLS-DA) show the differences between two groups. 

```{r echo=Ture}
#PCoA
library(vegan)
meta_dist=vegdist(meta,method="bray",binary = F)
meta_pcoa=cmdscale(meta_dist,k=3,eig = T)

meta_pcoa_points=as.data.frame(meta_pcoa$points)
sum_eig=sum(meta_pcoa$eig)
eig_percent=round(meta_pcoa$eig/sum_eig*100)
colnames(meta_pcoa_points)=paste0("PCoA",1:3)
meta_pcoa_result=cbind(meta_pcoa_points,group)
head(meta_pcoa_result)

library(ggplot2)
Fig1C=ggplot(meta_pcoa_result,aes(x=PCoA1,y=PCoA2,color=group))+
       labs(x=paste("PCoA1(",eig_percent[1],"%)",sep = ""),
            y=paste("PCoA2(",eig_percent[2],"%)",sep = ""))+
  scale_color_manual(values=c("DLY"="#4e62ab","JXB"="#d6404e"))+
         geom_point(size=4) + stat_ellipse(level=0.95)+
         theme_classic()+
  theme(axis.title = element_text(size = 32),
        axis.text = element_text(size = 24),
        legend.title = element_blank(),
        legend.position = c(0.95,0.95))
```

```{r echo=Ture}
#OPLS-DA
library(ropls) # PCA, PLS(-DA) and OPLS(-DA) for multivariate analysis and feature selection of omics data
library(ggforce) # Accelerating 'ggplot2'
library(ggprism) # A 'ggplot2' Extension Inspired by 'GraphPad Prism'



df1_oplsda <- opls(meta, group$group, predI = 5, orthoI = 0)

data <- as.data.frame(df1_oplsda@scoreMN)
o1 <- df1_oplsda@orthoScoreMN[,1]
data$o1 <- o1
data$group = group$group
data$samples = rownames(data)

x_lab <- df1_oplsda@modelDF[1, "R2X"] * 100
y_lab <- df1_oplsda@modelDF[2, "R2X"] * 100


col=c("DLY"="#4e62ab","JXB"="#d6404e")
Fig1D = ggplot(data,aes(x=p1,y=p2,color=group))+
  theme_bw()+
  geom_point(size=3)+
  theme(panel.grid = element_blank())+
  geom_vline(xintercept = 0,lty="dashed",color="grey")+
  geom_hline(yintercept = 0,lty="dashed",color="grey")+
  labs(x=paste0("P1 (",x_lab,"%)"),
       y=paste0("P2(",y_lab,"%)"))+
  stat_ellipse(data=data,
               geom = "polygon",level = 0.95,
               linetype = 2,size=0.5,
               aes(fill=group),
               alpha=0.2,
               show.legend = T)+
  scale_color_manual(values = col) +
  scale_fill_manual(values = c("DLY"="#4e62ab","JXB"="#d6404e"))+
  theme(axis.title.x=element_text(size=18),
        axis.title.y=element_text(size=18,angle=90),
        axis.text.y=element_text(size=10),
        axis.text.x=element_text(size=10),
        panel.grid=element_blank(),
        plot.title = element_text(size = 20, hjust = 0.5)) + 
  ggtitle("PLS-DA")


Fig1D
```

#e  Bacteroidetes/Firmicutes ratio

(E) The ratio of Bacteroidetes to Firmicutes in two groups. The data are presented as the means ± SEMs (standard error of the mean).
This figure is manually drawn by Graph Pad.

#f Stack diagram

(F) The relative abundance of the gut flora at the phylum level by stacked plot.
This figure is manually drawn by Graph Pad.

#g LEfSe

(G) The differences in community composition between two groups by LEfSe analysis. Nodes with different colors in the figure represent significant effects on the differences between groups, and the yellow nodes indicate microbial taxa without significant changes. The column displays biomarkers at LDA > 3.
This figure is drawn by Majorbio (Shanghai, China)

#h Co-occurance network

(H) Visual network and topology statistics of microbial co‐occurrence in the two groups. LDA: Linear Discriminant Analysis effect size.

```{r echo=Ture}
p_list = c("ggplot2", "BiocManager", "devtools", "igraph", "network", "sna", "tidyverse","tidyfst","ggnewscale","ggClusterNet","phyloseq")
for(p in p_list){if (!requireNamespace(p)){install.packages(p)}
  library(p, character.only = TRUE, quietly = TRUE, warn.conflicts = FALSE)}



library(ggClusterNet)
library(phyloseq)
library(tidyverse)
library(igraph)
library(sna)
library(network)

file="./metagenomic raw data (genus).xlsx"
otutable <- read.xlsx(file,1,header=T,row.names=1)

taxnomoy <- read.xlsx(file,3,header=T,row.names=1)
group <- read.xlsx(file,4,header=T)
group <- as.data.frame(group[c(1:5),])
rownames(group)=group[,1] 
group=group[,-1,drop=F]

otutable <- otutable[rowSums(otutable) != 0, ]



taxnomoy <- taxnomoy[rownames(otutable), ]
taxnomoy=as.data.frame(taxnomoy)
rownames(taxnomoy)=rownames(otutable)


ps <- phyloseq(tax_table(as.matrix(taxnomoy)),otu_table(as.matrix(otutable),taxa_are_rows = T),sample_data(group))



path = "./co-occurance network"
dir.create(path)
map = sample_data(ps)
map$Group = "one"
sample_data(ps) = map
result = network.2(ps = ps,
                   N = 1000,
                   big = TRUE,
                   maxnode = 5,
                   select_layout = TRUE,
                   layout_net = "model_igraph",
                   r.threshold=0.4,
                   p.threshold=0.01,
                   label = FALSE,
                   path = path,
                   zipi = FALSE)

p = result[[1]]
data = result[[2]]
num= 3

plotname1 = paste(path,"/network_all.pdf",sep = "")
ggsave(plotname1, p,width = 16*num,height = 16,limitsize = FALSE)

tablename <- paste(path,"/co-occurrence_Grobel_net",".csv",sep = "")
write.csv(data,tablename)

#next, using Gephi for drawing network

```

