---
title: Figure S1 ARGs (Antibiotic resistance genes) differ between the two pig breeds
  (N = 5 for each group).
author: "Liang Huang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Set output directory
output_dir="./"
```

#a and b Alpha diversity

(A) Alpha diversity of ARGs compared by Shannon and (B) Simpson indices. 

```{r}
library(phyloseq)
library(vegan)
library(xlsx)
file="./ARGs DATA.xlsx"
meta=read.xlsx(file,1,header=T,row.names=1)
meta=meta[,c(1:10)]
meta=t(meta)
meta=as.data.frame(meta)
group=read.xlsx(file,2,header=T,row.names=1)



shannon <- diversity(meta, index = "shannon")
shannon=as.data.frame(shannon)
df <- data.frame(shannon, Group = group$group)
write.xlsx(df,"./alpha_shannon.xlsx")


simpson <- diversity(meta, index = "simpson")
simpson=as.data.frame(simpson)
df <- data.frame(simpson, Group = group$group)
write.xlsx(df,"./alpha_simpson.xlsx")

# This figure is manually drawn by Graph Pad using data above.
```

#c PCoA

(C) PCoA analysis showed differential beta diversity between the two groups.

```{r}
library(vegan)
meta_dist=vegdist(meta,method="bray",binary = F)
meta_pcoa=cmdscale(meta_dist,k=3,eig = T)

meta_pcoa_points=as.data.frame(meta_pcoa$points)
sum_eig=sum(meta_pcoa$eig)
eig_percent=round(meta_pcoa$eig/sum_eig*100)
colnames(meta_pcoa_points)=paste0("PCoA",1:3)
meta_pcoa_result=cbind(meta_pcoa_points,group)
head(meta_pcoa_result)

library(ggplot2)
Fig1C=ggplot(meta_pcoa_result,aes(x=PCoA1,y=PCoA2,color=group))+
       labs(x=paste("PCoA1(",eig_percent[1],"%)",sep = ""),
            y=paste("PCoA2(",eig_percent[2],"%)",sep = ""))+
  scale_color_manual(values=c("DLY"="#4e62ab","JXB"="#d6404e"))+
         geom_point(size=4) + stat_ellipse(level=0.95)+
         theme_classic()+
  theme(axis.title = element_text(size = 32),
        axis.text = element_text(size = 24),
        legend.title = element_blank(),
        legend.position = c(0.95,0.95))
```

#d Stack diagram

(D) Stack diagram displaying the top 10 antibiotic types in each pig. * with red indicates up-regulated genes in the JXB group, * with blue indicates down-regulated genes.
This figure was drawn by using Graph Pad.

#e and f Co-occurance network

(E) The co-occurrence networks among ARGs in the DLY and (F) in the JXB. Red and blue edges represent positive and negative correlations, respectively, between nodes.

```{r}
library(ggClusterNet)
library(phyloseq)
library(tidyverse)
library(igraph)
library(sna)
library(network)
library(xlsx)

file="./ARGs DATA.xlsx"


#########Co-occurance in JXB pig########
otutable <- read.xlsx(file,3,header=T,row.names=1)
metadata <- read.xlsx(file,4,header=T,row.names=1)

taxnomoy <- read.xlsx(file,1,header=T,row.names=1)

otutable <- otutable[rowSums(otutable) != 0, ]

taxnomoy <- taxnomoy[rownames(otutable), ]
taxnomoy <- taxnomoy[,1]
taxnomoy=as.data.frame(taxnomoy)
rownames(taxnomoy)=rownames(otutable)
colnames(taxnomoy)[1]="Phylum"

ps <- phyloseq(tax_table(as.matrix(taxnomoy)),otu_table(as.matrix(otutable),taxa_are_rows = T),sample_data(metadata))



path = "./JXB"
dir.create(path)
map = sample_data(ps)
map$Group = "one"
sample_data(ps) = map
result = network.2(ps = ps,
                   N = 100,
                   big = F,#是否大于300
                   maxnode = 5,
                   select_layout = TRUE,
                   layout_net = "model_igraph",
                   r.threshold=0.4,
                   p.threshold=0.05,
                   label = FALSE,
                   path = path,
                   zipi = FALSE)

# 多组网络绘制到一个面板
p = result[[1]]
# 全部样本网络参数比对
data = result[[2]]
num= 3
# plotname1 = paste(path,"/network_all.jpg",sep = "")
# ggsave(plotname1, p,width = 16*num,height = 16,dpi = 72)

plotname1 = paste(path,"/network_JXB.pdf",sep = "")
ggsave(plotname1, p,width = 16*num,height = 16,limitsize = FALSE)

tablename <- paste(path,"/co-occurrence_JXB_net",".csv",sep = "")
write.csv(data,tablename)



#########Co-occurance in DLY pig########
otutable <- read.xlsx(file,5,header=T,row.names=1)
metadata <- read.xlsx(file,6,header=T,row.names=1)

taxnomoy <- read.xlsx(file,1,header=T,row.names=1)

otutable <- otutable[rowSums(otutable) != 0, ]

taxnomoy <- taxnomoy[rownames(otutable), ]
taxnomoy <- taxnomoy[,1]
taxnomoy=as.data.frame(taxnomoy)
rownames(taxnomoy)=rownames(otutable)
colnames(taxnomoy)[1]="Phylum"

ps <- phyloseq(tax_table(as.matrix(taxnomoy)),otu_table(as.matrix(otutable),taxa_are_rows = T),sample_data(metadata))



path = "./DLY"
dir.create(path)
map = sample_data(ps)
map$Group = "one"
sample_data(ps) = map
result = network.2(ps = ps,
                   N = 100,
                   big = F,#是否大于300
                   maxnode = 5,
                   select_layout = TRUE,
                   layout_net = "model_igraph",
                   r.threshold=0.4,
                   p.threshold=0.05,
                   label = FALSE,
                   path = path,
                   zipi = FALSE)

# 多组网络绘制到一个面板
p = result[[1]]
# 全部样本网络参数比对
data = result[[2]]
num= 3
# plotname1 = paste(path,"/network_all.jpg",sep = "")
# ggsave(plotname1, p,width = 16*num,height = 16,dpi = 72)

plotname1 = paste(path,"/network_DLY.pdf",sep = "")
ggsave(plotname1, p,width = 16*num,height = 16,limitsize = FALSE)

tablename <- paste(path,"/co-occurrence_DLY_net",".csv",sep = "")
write.csv(data,tablename)
```
These figures were finally drawn by using Cytoscape.


#g and h 

(G) Random forest filtered the top 30 most important antibiotic types in the two pig breeds and (H) the ROC. 

```{r}
BiocManager::install("pROC")
library(randomForest)
library(caret)
library(pROC)
library(xlsx)
file="./ARGs DATA.xlsx"
df=read.xlsx(file,2,header=T,row.names=1)
dim(df)

#将数据随机分为训练集和测试集
trainlist=createDataPartition(df$group,p=0.6,list = F)#0.6表示提取60%的数据用于训练模型
trainset=df[trainlist,]
testset=df[-trainlist,]

#1.build model，使用训练集构建模型
set.seed(123)
rf.train=randomForest(as.factor(group)~.,data=trainset,importance=T,na.action = na.pass)
rf.train
plot(rf.train,main="randomforest origin")


set=importance(rf.train)
varImpPlot(rf.train)
write.xlsx(set,"./top30 importance microbiota.xlsx")

#2.测试集数据预测
set.seed(456)
rf.test=predict(rf.train,newdata = testset,type = "class")
rf.test

rf.cf=caret::confusionMatrix(as.factor(rf.test),as.factor(testset$group))

#3.ROC,AUC
rf.test2=predict(rf.train,newdata = testset,type="prob")

roc.rf=multiclass.roc(testset$group, rf.test2)

roc.rf_1=multiclass.roc(testset$group, rf.test2[,1])


plot(roc.rf_1$rocs[[1]],col="blue")
plot(roc.rf_1$rocs[[2]],add=T,col="red")
auc(roc.rf_1)

```

#i Heatmap

(H) The ROC and (I) abundance heatmap of these genes are shown.

```{r}
library(pheatmap)
library(xlsx)
file = "./Top 30.xlsx"
data=read.xlsx(file,1,header=T,row.names=1)

Groups=read.xlsx(file,2,header=T,row.names=1)
Groups$group <- factor(Groups$group, levels = unique(Groups$group))

data=na.omit(data)
data <- data[apply(data, 1, function(row) !all(row == 0)), ]

library(pheatmap)
p=pheatmap(data,
         cluster_rows=T,
         clustering_method = "complete",
         cluster_cols = F,
         border_color = NA,
         #cellwidth = 15, cellheight = 15,
         #clustering_distance_rows = "eulidean",
         #clustering_method = "complete",
         #cutree_rows = "2",
         annotation_col = Groups,
         legend = TRUE,
         #legend_breaks = unique(Groups$Group),
         #legend_labels = unique(Groups$Group),
         annotation_names_col = T,
         labels_col = colnames(data),
         annotation_legend = T,
         show_rownames = T,
         fontsize_row = 8,
         show_colnames = T,
         #fontsize_col=10,
         angle_col = 0,
         #main = "",
         scale="row",
         color = colorRampPalette(c("#5596e0","#ffffff","#FF0000"))(100))
```

